Concave reduction of swarm voids

### 2018-06-05 paper.tex
Updates

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=4cm]{figures/PerimeterBotsCircle4}
{Void reduction result\label{fig:InnerPerimeter3}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=4cm]{figures/PerimeterBotsCircle1}
{Outer Perimeter\label{fig:OuterPerimeter2}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=4cm]{figures/PerimeterBotsCircle2}
{Void reduction result\label{fig:OuterPerimeter3}}

@@

\section{Concave reduction implementation}\label{sec:ConcaveReductionImp}
Detection of a swarm's perimeter can be used for several swarming effects in addition to concave reduction such as reducing the sensor requirements to coordinate a swarm to a destination. Identifying agents that are suitable for concave reduction involves the same conditional checks as the perimeter detection algorithm with the addition of a status check on the \textit{cyclic-angular-check} component.

>>>>

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=4cm]{figures/PerimeterBotsCircle4}
{Concave reduction result\label{fig:InnerPerimeter3}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=4cm]{figures/PerimeterBotsCircle1}
{Outer Perimeter (swarm without voids)\label{fig:OuterPerimeter2}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=4cm]{figures/PerimeterBotsCircle2}
{Concave reduction result (swarm without voids)\label{fig:OuterPerimeter3}}

@@

\section{Concave reduction implementation}\label{sec:ConcaveReductionImp}
A swarm's perimeter can be used to modify its behaviour, such as reducing the sensor requirements to coordinate a swarm to a destination. Identifying agents that are suitable for concave reduction involves the same conditional checks as the perimeter detection algorithm with the addition of a status check on the \textit{cyclic-angular-check} component.
